\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Mohammed Saif} \\ \vspace{1pt}
    \small +91 7075103874 $|$ \href{mailto:saifmujeeb2603@gmail.com}{\underline{saifmujeeb2603@gmail.com}} $|$ 
    \href{https://linkedin.com/in/mohammed-saif-a6097b227}{\underline{linkedin.com/in/mohammed-saif}} $|$
    \href{https://github.com/saifxyzyz}{\underline{github.com/saifxyzyz}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rootz Communication}{Remote}
      {Machine Learning Intern}{Aug 2024 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Developed Python automation scripts to streamline inventory management and purchase order processing, reducing manual workload.}
        \resumeItem{Managed DNS and hosting configurations for 3+ domains on the GoDaddy platform.}
        \resumeItem{Visualized ad campaign performance metrics (impressions, clicks, CTR) by building dashboards using the Agency Analytics Tool.}
      \resumeItemListEnd

    \resumeSubheading
      {YHills}{Hyderabad, India}
      {Machine Learning Engineer}{Mar 2024 -- Jun 2024}
      \resumeItemListStart
        \resumeItem{Implemented Machine Learning models using Python, specifically utilizing Random Forest and Naive Bayes classifiers.}
        \resumeItem{Conducted data preprocessing and analysis to optimize model accuracy for predictive tasks.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{WordSmith} $|$ \emph{Python, PyTorch, Transformers, PEFT, HuggingFace}}{}
      \resumeItemListStart
        \resumeItem{Developed a Generative AI model fine-tuned on the Gemma 270m architecture to generate professional emails.}
        \resumeItem{Utilized Parameter Efficient Fine-Tuning (PEFT) and HuggingFace Transformers to optimize training performance.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Automated Segregator} $|$ \emph{Python, SMTP, IMAP, Openpyxl}}{}
      \resumeItemListStart
        \resumeItem{Built a Python automation tool to handle inventory management and automated report generation.}
        \resumeItem{Integrated IMAP and SMTP libraries for email handling and Openpyxl for Excel file manipulation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript, TypeScript, SQL, HTML, CSS} \\
     \textbf{Frameworks/Libraries}{: PyTorch, TensorFlow, Flask, Django, Scikit-learn, XGBoost, Pandas, NumPy, React.js, Node.js} \\
     \textbf{Cloud \& Tools}{: Google Cloud Platform (GCP), AWS EC2, Azure, Firebase, MongoDB, Linux, Git} \\
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Scientific Computing with Python} -- FreeCodeCamp \\
     \textbf{Google Analytics Certification} -- Google \\
     \textbf{Power BI Bootcamp} -- LetsUpgrade
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Osmania University}{Hyderabad, India}
      {Bachelor of Engineering in Computer Science; CGPA: 7.8/10}{2021 -- 2025}
  \resumeSubHeadingListEnd



\end{document}
